### 2022-09-28 main/chapter_context.tex
add persint manual

@@

\begin{figure}[tp]
\centering
\includegraphics[width=0.6\textwidth]{figures/atlas_cutaway_volume_1.pdf}
\caption[
A central slice of \atlas's design
]{%
A central slice of \atlas's design, reproduced from~\cite{atlas1999design1},
including a simulated event that interacts with several sensitive subsystems.
}
\label{fig:atlas_cutaway}
\end{figure}

>>>>

\TODO{split chapters again}

@@

\begin{figure}[tp]
\centering
\includegraphics[width=0.6\textwidth]{figures/atlas_cutaway_volume_1.pdf}
\caption[
A central slice of \atlas's design
]{%
A central slice of \atlas's design, reproduced from~\cite{atlas1999design1,
persint2014manual},
including a simulated event that interacts with several sensitive subsystems.
}
\label{fig:atlas_cutaway}
\end{figure}
